\center \fontsize{18.8}{20} \selectfont Towards Globally Color-Dual All-Loop Integrands

### 2023-09-12 notes/2loopNLSM.tex
Edited color dual boostrap section

\subsection{Color-dual Bootstrap}
\label{sec:bootstrap}
Some background here on how we approach color-dual bootstrap (as we will utilize in our two-loop construction). Building an ansatz from irreducible lorentz products (ISPs). Comments about:
\begin{itemize}
\item loop momenta weight counting 
\item polynomial vector spaces 
\item generalized gauge freedom
\item functional jacobi constraints and cuts
\end{itemize}

As part of attemtping to construct a color-kinematics dual
representation for $\mathcal{N}=0$ Yang--Mills at two loops, Bern,
Davies, and Nohle (BDN) \cite{Bern:2015ooa} lay out the following core
assumptions in searching for double-copyable integrand numerators (ordered according to the
reference):
\begin{enumerate}
\item \textbf{Locality}: Diagram ``numerators'' are polynomials in momenta and
  polarizations, \eg the diagrams only have poles given by the
  propagators of the diagrams.
\item  \textbf{Power-counting:} The maximum power of the loop momenta in the
  numerator is bounded by Feynman-gauge Feynman rules.
\item  \textbf{Cubic diagrams}: The only diagrams with nonzero numerators are
  those with strictly cubic vertices.  This is generally a requirement
  to properly define the kinematic Jacobi relations.
\item  \textbf{Symmetries}: The diagram numerators are only a function of the
  diagram's topology and labeling. The diagram numerators are invariant under the
  automorphisms of the diagrams \emph{including signs that compensate
    for color-factor sign changes}.
\item  \textbf{Unitarity cuts}: The cuts of the ansatz must reproduce the
  physical unitarity cuts of the theory.
\item  \textbf{Color-kinematics duality}: The numerators obey some form of the
  kinematic Jacobi relations.
\end{enumerate}
Point 1 is generally a matter of convenience: there are many examples
in which ``numerators'' with controlled rational contributions have
been found
\cite{Square,WeinzierlBCJLagrangian,Mogull:2015adi,FivePointN4BCJ,Johansson:2017bfl}.
However, without a guiding principle about what types of rational
terms to use, the size of ans\"{a}tze quickly get out of hand.  Point
2 was motivated at the time by the hope that color-dual numerators
could arise naturally out of a special gauge choice. \jm{I'm not sure
  that we should bring up point 2.  I don't follow it and I don't
  think Alex did either since this wouldn't be the most general
  ansatz.  Also, why doesn't point 5 cover point 4?}\ace{I paraphrased
  these out of \cite{Bern:2015ooa}, thus the inclusion of Point 2.
  For Points 4 and 5, definitely 4 $\not \Rightarrow$ 5.  In the other
  direction, I could imagine a situation in which we violate 4 (eg we
  need to specify a reference ordering) but that symmetries are still
  respected as long as you also perform the correct actions on the
  auxiliary data.} On the other hand, recent work by Ben-Shahar,
Garozzo, and Johansson \cite{Ben-Shahar:2022ixa} \ace{Are there other
  good examples?}  demonstrates that constructing Feynman rules which
produce manifestly color-dual numerators for the NMHV sector of
Yang--Mills requires introducing additional auxiliary fields,
including higher-spin modes, which could shift the expected power
counting in non-trivial ways.  Point 3 is a requirement of the BCJ
double-copy: currently there is no known way of incorporating
non-cubic diagrams into the kinematic Jacobi relations.  Points 4 and
5 will be elaborated on in \cref{sec:syms}, Point 6 in
\cref{sec:unitarity}, and Point 7 in \cref{sec:jac-rels}.

References for Jacobi, unitarity, etc.

Aside from the few special theories mentioned in \cref{sec:CKLagrangians}, color-dual integrands are constructed from an ansatz.

@@

Color-kinematics duality is stated in terms of cubic graphs so the
first step is to express in the integrand in terms of such graphs.  As
an example we will focus on the 4pt 2-loop integrand of some
color-dual theory like NLSM or YM.  The 4pt 1-loop integrand is not a
sufficiently illustrative example because, for instance, it lacks any
self Jacobi like \cref{eq:TwoLoopJacobiTwo} to be discussed shortly.
Naively there are 14 cubic 4pt 2-loop topologies ignoring tadpoles and
bubble on external leg (BEL) graphs.  It is always possible to express
an integrand in terms of cubic graphs, even for an even valency theory
like NLSM, by multiplying and dividing the integrand by factors of
inverse propagators.  Next, the ansatz must have the correct power
counting and external states, \emph{e.g.}, polarization vectors for
YM.  The numerator is assumed to be manifestly local but one approach
to finding color-dual numerators is to relax manifest locality, see
(...) for more details.  After zeroth order considerations like power
counting, there are three conditions that are imposed on the ansatz:
(1) Jacobi relations amongst graphs must be satisfied, (2) numerators
must respect graph symmetries, and (3) the integrand must have the
correct unitarity cuts.

(These three constraints can be solved in any order and my guess is that Alex and I did solve them in different orders.)

\paragraph{Jacobi relations}
\label{sec:jac-rels}

@@

\paragraph{Graph symmetries}
\label{sec:syms}

@@

\paragraph{Unitarity}
\label{sec:unitarity}
The last key source of constraints comes from ensuring that the ansatz
correctly reproduces the generalized unitarity cuts of the theory.
Matching the unitarity cuts provides the vast majority of
theory-dependent information for the ansatz by ensuring that the
numerators under construction are actually a valid representation of
the theory being considered.  Generalized unitarity methods has been
reviewed in many places \cite{BCFUnitarity, BernHuangReview,
  Bern:2015ooa, Bourjaily:2017wjl, JJHenrikReview, FivePointN4BCJ,
  Bern:2012uf, BCJreview, Edison:2022jln} \ace{Here is a semi-random
  collection of unitarity-related citations.  Probably want to bulk it
  up a bit more} so we will be light on details here. We also want to
call special attention to Ref.~\cite{Carrasco:2023qgz} for a recent
treatment of unitarity methods optimized for even multiplicity
theories like NLSM.

>>>>

\subsection{Color-dual Bootstrap}
\label{sec:bootstrap}

Aside from a few special theories \citepls{}, color-dual integrands are constructed from an ansatz.
The four conditions imposed on the ansatz are summarized here and elaborated on below.
\begin{enumerate}
\item \textbf{Locality}: Diagram ``numerators'' are polynomials in momenta and
  polarizations, \eg the diagrams only have poles given by the
  propagators of the diagrams.
  \item  \textbf{Color-kinematics duality}: The numerators obey the same Jacobi identities as the color factors.
This implicitly requires that the integrand is expressed in terms of purely cubic diagrams.
\item  \textbf{Graph symmetries}: The diagram numerators are invariant under the automorphisms of the diagrams \emph{including signs that compensate for color-factor sign changes}.
The diagram numerators are only a function of the diagram's topology and labeling.
\item  \textbf{Unitarity cuts}: The cuts of the ansatz must reproduce the physical unitarity cuts of the theory.
\end{enumerate}

\paragraph{Locality}

The kinematic numerators need to be $D$-dimensional, Lorentz invariant, local (polynomial) functions of the graph kinematics with the correct power counting and external states.
Insisting on a local numerator is partly a matter of convenience as the ansatz for a rational function would quickly grow out of control without a guiding principle for what terms to include.
Locality is also physically motivated since Feynman rules typically produce polynomial numerators.
While locality is well motivated from a physical and computational standpoint, the literature has featured numerators that violate locality, break manifest Lorentz invariance, and modify naive power counting through the presence of higher spin modes \cite{Square, WeinzierlBCJLagrangian, Mogull:2015adi, FivePointN4BCJ, Johansson:2017bfl, Ben-Shahar:2022ixa, Cheung:2016prv, Cheung:2021zvb}. \jm{Alex wrote some of this citation.  I'm not sure why it broke.}
These developments suggest that relaxing locality is a viable option when the condition proves too stringent for an ansatz.
We will comment more on locality in \sect{}.

\paragraph{Color-kinematics duality}

Somewhere emphasize that Zvi et al didn't do the most general ansatz, imposed extra loop power counting constraints.

@@

Color-kinematics duality is stated in terms of cubic graphs so the
first step is to express in the integrand in terms of such graphs.  As
an example we will focus on the 4pt 2-loop integrand of some
color-dual theory like NLSM or YM.  The 4pt 1-loop integrand is not a
sufficiently illustrative example because, for instance, it lacks any
self Jacobi like \cref{eq:TwoLoopJacobiTwo} to be discussed shortly.
Naively there are 14 cubic 4pt 2-loop topologies ignoring tadpoles and
bubble on external leg (BEL) graphs.  It is always possible to express
an integrand in terms of cubic graphs, even for an even valency theory
like NLSM, by multiplying and dividing the integrand by factors of
inverse propagators.  Next, the ansatz must have the correct power
counting and external states, \emph{e.g.}, polarization vectors for
YM.  The numerator is assumed to be manifestly local but one approach
to finding color-dual numerators is to relax manifest locality, see
(...) for more details.

@@

\paragraph{Graph symmetries}

Want explicit Bose sym, broken in many cases.

@@

\paragraph{Unitarity}

The last key source of constraints comes from ensuring that the ansatz
correctly reproduces the generalized unitarity cuts of the theory.
Matching the unitarity cuts provides the vast majority of
theory-dependent information for the ansatz by ensuring that the
numerators under construction are actually a valid representation of
the theory being considered.  Generalized unitarity methods has been
reviewed in many places \cite{BCFUnitarity, BernHuangReview,
  Bern:2015ooa, Bourjaily:2017wjl, JJHenrikReview, FivePointN4BCJ,
  Bern:2012uf, BCJreview, Edison:2022jln} \ace{Here is a semi-random
  collection of unitarity-related citations.  Probably want to bulk it
  up a bit more} so we will be light on details here. We also want to
call special attention to Ref.~\cite{Carrasco:2023qgz} for a recent
treatment of unitarity methods optimized for even multiplicity
theories like NLSM.
